---
title: "COVID-19 Total Cases and Estimates of Active Cases"
author: "C. Lange, Department of Economics, California State Polytechnic University, Pomona"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cerulean
    highlight: kate
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: true
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(knitr)
library(plotly)
library(cowplot)
read_chunk("ScriptMain.R")
```

```{r Setup, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

```


```{r child="../Header.txt"}

```

# Introduction

```{r child="../Intro.txt"}

```

# `r CurrentState`

## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCasesState)
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCasesState)
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCasesState)
```

## Daily %-Change in Activ Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCasesState)
```

## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCasesState+labs(title=" "),
          PlotNewCasesState+labs(title=" "),
          PlotEstActCasesState+labs(title=" "),
          PlotGrowthRateEstActCasesState+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)

```

# `r CurrentCounties[1]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[1]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[1]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[1]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[1]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[1]]+labs(title=" "),
          PlotNewCases[[1]]+labs(title=" "),
          PlotEstActCases[[1]]+labs(title=" "),
          PlotGrowthRateEstActCases[[1]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[2]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[2]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[2]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[2]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[2]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[2]]+labs(title=" "),
          PlotNewCases[[2]]+labs(title=" "),
          PlotEstActCases[[2]]+labs(title=" "),
          PlotGrowthRateEstActCases[[2]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[3]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[3]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[3]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[3]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[3]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[3]]+labs(title=" "),
          PlotNewCases[[3]]+labs(title=" "),
          PlotEstActCases[[3]]+labs(title=" "),
          PlotGrowthRateEstActCases[[3]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[4]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[4]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[4]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[4]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[4]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[4]]+labs(title=" "),
          PlotNewCases[[4]]+labs(title=" "),
          PlotEstActCases[[4]]+labs(title=" "),
          PlotGrowthRateEstActCases[[4]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[5]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[5]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[5]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[5]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[5]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[5]]+labs(title=" "),
          PlotNewCases[[5]]+labs(title=" "),
          PlotEstActCases[[5]]+labs(title=" "),
          PlotGrowthRateEstActCases[[5]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[6]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[6]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[6]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[6]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[6]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[6]]+labs(title=" "),
          PlotNewCases[[6]]+labs(title=" "),
          PlotEstActCases[[6]]+labs(title=" "),
          PlotGrowthRateEstActCases[[6]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[7]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[7]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[7]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[7]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[7]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[7]]+labs(title=" "),
          PlotNewCases[[7]]+labs(title=" "),
          PlotEstActCases[[7]]+labs(title=" "),
          PlotGrowthRateEstActCases[[7]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[8]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[8]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[8]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[8]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[8]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[8]]+labs(title=" "),
          PlotNewCases[[8]]+labs(title=" "),
          PlotEstActCases[[8]]+labs(title=" "),
          PlotGrowthRateEstActCases[[8]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[9]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[9]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[9]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[9]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[9]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[9]]+labs(title=" "),
          PlotNewCases[[9]]+labs(title=" "),
          PlotEstActCases[[9]]+labs(title=" "),
          PlotGrowthRateEstActCases[[9]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```

# `r CurrentCounties[10]` County


## Accumulated Cases (Active and Not-Active)

```{r child="../TotalCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotTotalCases[[10]])
```

## Daily New Cases

```{r child="../NewCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotNewCases[[10]])
```

## Predicted Active Cases

```{r child="../EstActiveCases.txt"}

```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotEstActCases[[10]])
```

## Daily %-Change in Active Cases

```{r child="../PercGrowthEstActiveCases.txt"}

```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplotly(PlotGrowthRateEstActCases[[10]])
```


## Summary Charts

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_grid(PlotTotalCases[[10]]+labs(title=" "),
          PlotNewCases[[10]]+labs(title=" "),
          PlotEstActCases[[10]]+labs(title=" "),
          PlotGrowthRateEstActCases[[10]]+labs(title=" "),
          labels = c("Accumulated Cases",
                     "New Cases",
                     "Active Cases",
                     "%-Growth Active Cases"), size=10,
    ncol=2, nrow=2)
```
